BALANCING EVERYDAY TASKS AND PROJECT MANAGEMENT WITH EASE

### 2023-11-30 article.tex
Update article.tex

>>>>

\section{References}
[1] S. M. S. Islam and M. Rokonuzzaman, "Process centric work breakdown structure for easing Software Project management challenges: Business case analysis example," 2009 12th International Conference on Com- puters and Information Technology, Dhaka, Bangladesh, 2009, pp. 508-513, doi: 10.1109/ICCIT.2009.5407291\\
[2] S. Khan, S. Sharma, T. Singh and A. Juneja, "An Innovative Approach to Project Management and ePortals," 2023 International Conference on Computational Intelligence, Communication Technology and Networking (CICTN), Ghaziabad, India, 2023, pp. 359-363, doi: 10.1109/CICTN57981.2023.10140667.\\
[3] S. De and V. Vijayakumaran, "An E cient Algorithm in Project Management for Resource Schedul- ing and Conflict Management using Graph Coloring Technique," 2020 IEEE International Conference for Inno- vation in Technology (INOCON), Bangluru, India, 2020, pp. 1-6, doi: 10.1109/INOCON50539.2020.9298193.\\
[4] C. Nitin Rajadhyaksha and J. R. Saini, "Robotic Process Automation for Software Project Manage- ment," 2022 IEEE 7th International conference for Convergence in Technology (I2CT), Mumbai, India, 2022, pp. 1-5, doi: 10.1109/I2CT54291.2022.9823972.\\
[5] V. Considine, "Systems engineering and strategic project management," IEE Half-Day Colloquium on Systems Engineering in Strategic Management Planning (Digest No: 1997/141), London, UK, 1997, pp. 2/1-2/4, doi: 10.1049/ic:19970779.\\
[6] R. Leano, S. Chattopadhyay and A. Sarma, "What makes a task di cult? An empirical study of perceptions of task di culty," 2017 IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC), Raleigh, NC, USA, 2017, pp. 67-71, doi: 10.1109/VLHCC.2017.8103452.\\
[7] M. Svahnberg and A. Karasira, "A Study on the Importance of Order in Requirements Prioritisation," 2009 Third International Workshop on Software Product Management, Atlanta, GA, USA, 2009, pp. 35-41, doi: 10.1109/IWSPM.2009.1.\\
[8] Hobday, M. (2000b). The project-based organisation: an ideal form for managing complex products and systems? Research Policy, 29(7–8), 871–893. https://doi.org/10.1016/s0048-7333(00)00110-4\\
[9] Khatib, M. E., Kherbash, A., Qassimi, A. A., Mheiri, K. A. (2022d). How can collaborative work and collaborative systems drive operational excellence in project management? Journal of Service Science and Management, 15(03), 297–307. https://doi.org/10.4236/jssm.2022.153017\\
[10] Ellegård, K. (1999). A time-geographical approach to the study of everyday life of individuals - a challenge of complexity. GeoJournal, 48(3), 167–175. http://www.jstor.org/stable/41147368\\
